Generative adversarial neural networks model of photonic crystal fiber based Surface Plasmon Resonance Sensor

### 2020-10-06 docs/paper/paper.tex
update: revision list

@@

% The paper headers
\markboth{Journal of Journal of Lightwave Technology,~Vol.~14, No.~8, August~2015}%
{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for IEEE Journals}

@@

The cross section of the proposed structure is illustrated in Figure 3. As can be seen from this figure, the sensor consists of an analyte channel (sensing medium), plasmonic layer (Au)and various sized cladding air holes. The cladding region is formed by nineteen various sized air holes, sited on silica background with hexagonal lattice arrangement. The air hole diameters are set to;  $d_1$= $0.45 \mu m$, $d_2$= $0.75 \mu m$, $d_3$= $0.35 \mu m$, and  $d_c$= $0.15$. The distance between air holes ($\lambda$) are fixed to $2 \mu m$. Initially, trapping the light (fundamental mode) into the core region is vital for mode quality. On the other hand, some amount of light needs to be leaked towards the plasmonic layer, where the sensitivity measurement occurs. This is the key phenomenon for resonance phase matching occurrence. In this respect, the various sized cladding holes are employed for controlling the light guidance, where each set of air holes are affecting different propagation characteristics of the sensor. The Gold (Au) material is used as a plasmonic layer and set to be $40 \mu m$. The Johnson and Christy Data \cite{johnson1972optical} are used for the permittivity values. The Sellmeier Equation (Eq.(\ref{eqn1})) is used for calculating the refractive index of Silica material \cite{bjarklev2003PCF}.

@@

		\addlegendentry{Actual}
		\legend{}
		\end{axis}
		\end{tikzpicture}
		%
		\begin{tikzpicture}
		\begin{axis}[
		xlabel=$Wavelength(\lambda) $  $ in $  $ nm $ ($n_{analyte=1.35}$), 
		ylabel=$~$,
		grid=both,
		minor grid style={gray!25},
		major grid style={gray!25},
		width=0.48\textwidth,
		height=6cm,
		legend pos=north west
		]
		\addplot[
		only marks,
		mark size=2.9pt, mark=o, color=red, fill=red
		] 
		table[x={wave},y={predicted}]{data/wave_135_their.txt};
		\addlegendentry{\cite{paper0}}

@@

		\addplot[
		color=blue
		] 
		table[x={wave},y={real}]{data/wave_135_their.txt};
		\addlegendentry{Actual}
		\legend{}
		% our: 0.37049
		% their: 0.17491
		\end{axis}
		\end{tikzpicture}
		\caption{Configuration estimation on SPR dataset.}
	\end{subfigure}
	\caption{Testing results without GAN augmentation phase}
	\label{chart:perfnoaug}
\end{figure*}

@@

		%w/o: 0.18869
		%w/g: 0.11670

@@

		\addplot[
		color=blue
		] 
		table[x={wave},y={real}]{data/wave_133_aug.txt};
		\addlegendentry{Actual}
		\legend{}
		\end{axis}
		\end{tikzpicture}
		\caption{Configuration estimation on SPR dataset}
	\end{subfigure}
	\caption{GAN Phase experimental results}
	\label{chart:ganperf}
\end{figure*}

>>>>

\tikzstyle directed=[postaction={decorate,decoration={markings, 
		mark=at position 1 with {\arrow[arrowstyle]{stealth}}}}]

\tikzstyle arrowstyle=[scale=1]

@@

% The paper headers
\markboth{ Journal of Lightwave Technology,~Vol.~14, No.~8, August~2015}%
{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for IEEE Journals}

@@

The cross section of the proposed structure is illustrated in Figure 3. As can be seen from this figure, the sensor consists of an analyte channel (sensing medium), plasmonic layer (Au)and various sized cladding air holes. The cladding region is formed by nineteen various sized air holes, sited on silica background with hexagonal lattice arrangement. The air hole diameters are set to;  $d_1$= $0.45 \mu m$, $d_2$= $0.75 \mu m$, $d_3$= $0.35 \mu m$, and  $d_c$= $0.15$. The distance between air holes ($\Lambda$) are fixed to $2 \mu m$. Initially, trapping the light (fundamental mode) into the core region is vital for mode quality. On the other hand, some amount of light needs to be leaked towards the plasmonic layer, where the sensitivity measurement occurs. This is the key phenomenon for resonance phase matching occurrence. In this respect, the various sized cladding holes are employed for controlling the light guidance, where each set of air holes are affecting different propagation characteristics of the sensor. The Gold (Au) material is used as a plasmonic layer and set to be $40 \mu m$. The Johnson and Christy Data \cite{johnson1972optical} are used for the permittivity values. The Sellmeier Equation (Eq.(\ref{eqn1})) is used for calculating the refractive index of Silica material \cite{bjarklev2003PCF}.

@@

		\legend{}
				legend style={anchor=north east,draw=none,fill=none,font=\tiny, at={(axis cs:670,1.55)}},

		]

		\addlegendimage{first}\addlegendentry{\cite{paper0} MSE: 0.08721}
		\addlegendimage{second}\addlegendentry{Proposed MSE: 0.18869 }

		\end{axis}
		\end{tikzpicture}
		%
		\begin{tikzpicture}
		\begin{axis}[
		xlabel=$Wavelength(\lambda) $  $ in $  $ nm $ ($n_{analyte=1.35}$), 
		ylabel=$~$,
		grid=both,
		minor grid style={gray!25},
		major grid style={gray!25},
		width=0.48\textwidth,
		height=6cm,
		legend pos=north west
		]
		\addplot[
		only marks,
		mark size=2.9pt, mark=o, color=red, fill=red
		] 
		table[x={wave},y={predicted}]{data/wave_135_their.txt};
		\addlegendentry{\cite{paper0}}

@@

		\addplot[
		color=blue
		] 
		table[x={wave},y={real}]{data/wave_135_their.txt};
		\addlegendentry{Actual}
		\legend{}
		% our: 0.37049
		% their: 0.17491
		legend style={anchor=north west,draw=none,fill=none,font=\tiny, at={(axis cs:670,1.55)}},
		legend cell align=left,
		]

		\addlegendimage{first}\addlegendentry{\cite{paper0} MSE:0.17491}
		\addlegendimage{second}\addlegendentry{Proposed MSE:0.37049 }

		\end{axis}
		\end{tikzpicture}
		\caption{Configuration estimation on SPR dataset.}
	\end{subfigure}
	\caption{Testing results without GAN augmentation phase}
	\label{chart:perfnoaug}
\end{figure*}

@@

		%w/o: 0.18869
		%w/g: 0.11670
		legend style={anchor=north west,draw=none,fill=none,font=\tiny, at={(axis cs:690,1.55)}},

		]

		\addlegendimage{first}\addlegendentry{Without GAN:0.18869}
		\addlegendimage{second}\addlegendentry{With GAN:0.11670 }

@@

		\addplot[
		color=blue
		] 
		table[x={wave},y={real}]{data/wave_133_aug.txt};
		\addlegendentry{Actual}
		\legend{}
				legend style={anchor=north west,draw=none,fill=none,font=\small, at={(axis cs:690,1.55)}},

		]

		\addlegendimage{first}\addlegendentry{Without GAN:0.32373}
		\addlegendimage{second}\addlegendentry{With GAN:0.08664 }
		\end{axis}
		\end{tikzpicture}
		\caption{Configuration estimation on SPR dataset}
	\end{subfigure}
	\caption{GAN Phase experimental results}
	\label{chart:ganperf}
\end{figure*}
